    
I would like to extend my gratitude to my advisor Andreas Hanke who enthusiastically accepted me as his student. I am grateful for everything you've taught me, for the physics you introduced me to, but even more for teaching me how to be a researcher. You taught me how to engage in the work: slowly, carefully, and consistently. You taught me how to discriminate the intellectual endeavors that matter, and focus on them. For these and many more lessons, for believing in my potential even more than I did myself, and for all the time we've spent working together, I'm immensely grateful.

I would also like to thank the many mentors who profoundly influenced me, often by just being an example on how to do research, teach, and live. I would like to thank Richard Price, who early in my career infected me with his passion for physics. Matthew Benacquista, for introducing me to research for the first time. Holger Pletsch and Colin Clark for showing me what a healthy and productive work culture is. Soma Mukherjee, for always having her door and heart open for her students. Soumya Mohanty, for teaching me to work like Michelangelo, with a hammer and chisel. Mario Diaz, for going above and beyond to be a guide to his students, and for being a model for the well-rounded and compassionate academic that I aspire to be. I would particularly like to thank Joseph Romano for believing in me at a time when it was much needed. For taking my intellectual interests seriously, teaching me the "know how to solve every problem that has been solved" philosophy and for doing so much to guide me. To all these mentors, the lessons you taught me will forever be with me and I will continue to transmit them to my peers and my own students.

\newpage

\newgeometry{top=1in, bottom=1in, left=1in, right=1in}
\thispagestyle{fancy}
\setlength{\parindent}{0.5in}
\doublespacing


Thank you to my fellow graduate students who accompanied me in this journey. Thank you to Zuzanna, Wiktoria, and Kazia for being there not only as classmates, but as friends. To Richard for all of our stimulating conversations, all the coffees, for teaching me the value of discipline, and for throwing the best physics parties. To Alexandro, for inspiring me with your work ethic and always reassuring me that things would be alright. To Satzhan, for all those mornings with bicycle rides and quantum foundations discussions. To Francisco, for the unconditional support and camaraderie. To Luis, for helping create the office culture I always tried to built. To Wendy, for all those moments when we shared our struggles. Your openness to even admit them validates me and inspires me to be more open myself. To Alejandro for giving me a home and a friend when I needed them most, and for all of our travels and adventures together. May there be many more.

Thank you to all my friends who supported me along the way. I am grateful to have too many to name, but you know this is for you. Thank you for sitting next to me while I worked when I didn't have time to share otherwise. Thank for cooking, living, traveling, playing music, and laughing with me. You kept my life balanced and more importantly, full of joy. 

Finally, thank you to my family. To my sister Genesis and mother Veronica for all of your love and support.


\restoregeometry

